Databases are an effective and efficient method for storage and access of mass-spectrometry data

### 2025-02-28 manuscript/manuscript.Rmd
Adding filename explicitly

cd java_things
curl -O https://dlcdn.apache.org/maven/maven-3/3.9.9/binaries/apache-maven-3.9.9-bin.zip
tar -xf apache-maven-3.9.9-bin.zip
git clone https://github.com/optimusmoose/MZTree.git
cd MZTree
cd msDataServer
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar java_things\MZTree\msDataServer\target\msDataServer-1.0.jar
(manually) open mztree file in port 4568

git clone https://github.com/yrm9837/mzMD-java.git
cd mzMD-java
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar java_things\mzMD-java\target\msDataServer-1.0.jar
(manually) open mzmd file in port 4567

>>>>

cd java_things
curl -O https://dlcdn.apache.org/maven/maven-3/3.9.9/binaries/apache-maven-3.9.9-bin.zip
tar -xf apache-maven-3.9.9-bin.zip
git clone https://github.com/optimusmoose/MZTree.git
cd MZTree
cd msDataServer
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar java_things\MZTree\msDataServer\target\msDataServer-1.0.jar
(manually) open mztree file in port 4568 (20220923_LEAP-POS_QC04.mzTree)

git clone https://github.com/yrm9837/mzMD-java.git
cd mzMD-java
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar java_things\mzMD-java\target\msDataServer-1.0.jar
(manually) open mzmd file in port 4567 (20220923_LEAP-POS_QC04.mzMD)
